The Concurrent Calculi Formalisation Benchmark

### 2024-02-21 short-paper/short-paper.tex
Add a comment for clarity.

% We previously promise to discuss combinations of techniques and applications to more elaborate schemes
\section{Going Beyond the Challenge Problems}\label{sec:going-beyond}
Our benchmark challenges do not cover all issues in the field, but focus on the fundamental textbook aspects of linearity, scope extrusion, and coinduction.
Many mechanisations need to combine techniques to handle several of these aspects, and some may also need to handle aspects that are not covered by our benchmark challenges at all.

>>>>

% We previously promise to discuss combinations of techniques and applications to more elaborate schemes
\section{Going Beyond the Challenge Problems}\label{sec:going-beyond}
\todo{Clean up this section to be more coherent.}
Our benchmark challenges do not cover all issues in the field, but focus on the fundamental textbook aspects of linearity, scope extrusion, and coinduction.
Many mechanisations need to combine techniques to handle several of these aspects, and some may also need to handle aspects that are not covered by our benchmark challenges at all.
